---
title: "HERMES QUALITY CONTROL"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HERMES QUALITY CONTROL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Required R libraries
```{r setup}
library(argparse)
library(cli)
library(data.table)
library(ggplot2)
library(viridis)
```

```{r setup2, include=FALSE}
script_path <- here::here("scripts", "gwas_qc.R")
Sys.setenv(QC_SCRIPT = script_path)
```

## Script location
https://github.com/nicksunderland/heRmes/blob/main/scripts/gwas_qc.R

## QC script inputs  
The QC script input parameters can be seen by calling the script with the `--help` flag.

```{bash call, echo=TRUE, eval = TRUE}
Rscript $QC_SCRIPT --help
```

## Reviewer QC input controls
The main required inputs required are in the table below, we likely will need to add more.

| Arg                 | Type   | Source                                   | Expose to UI |
|---------------------|--------|------------------------------------------|--------------|
| --gwas              | string | uploaded gwas file                       | NA           |
| --ref               | string | static ancestry-specific reference file  | NA           |
| --out               | string | output directory to write file and .pngs | NA           |
| --gwas_[colname]    | string | standard column names from mapping       | NA           |
| --ref_[colname]     | string | standard column names from reference file| NA           |
| --no_indel_alleles  | bool   | reviewer QC user interface               | Yes          |
| --freq_diff         | num    | reviewer QC user interface               | Yes          |
| --genomic_control   | bool   | reviewer QC user interface               | Yes          |
| --info_thresh       | num    | reviewer QC user interface               | Yes          |

## Example QC script call
```{bash file = here::here("scripts", "qc_test.sh"), eval=F}

```

## QC script  
The quality control procedure code is presented below.

```{r file = here::here("scripts", "gwas_qc.R"), eval=F}

```

